---
title: "Homework 7"
author: "Brayan Duran Medina"
output: html_document
---

# CONSOLIDATION EXCERCISE 1: choropleth maps

1 - Read “violence_women.csv” file into R.

2 - Join the csv data to your world sf object.

3 - Replace NA values in column value with zeros. Hint:

shp_violence$Value[is.na(shp_violence$Value)] <- 0

4 - Create some pretty breaks for your data, as the ones in the image below. Equal 0 to No Data.

5 - Create a color palette for your map and plot in showing only the cases of Europe, as in the image below.

6 - Save your map as an image.

```{r, cache=TRUE}
library(tidyverse)
library(giscoR)
library(sf)
library(classInt)
library(ggplot2)
library(RColorBrewer)

violence_w <- read.csv("data/violence_women.csv")

res <- "03"
target_crs <- 4326
world <- gisco_get_countries(resolution = res, epsg = target_crs)
world <- left_join(world, violence_w, by = c("ISO3_CODE" = "ISO3_CODE"))

world$Value[is.na(world$Value)] <- 0

breaks <- c(-0.01, 0, 10, 15, 20, 25, 30, 35, 100)
labels <- c("No Data", "<10%", "10-15%", "15-20%", "20-25%", "25-30%", "30-35%", ">35%")

palette <- brewer.pal(n = 7, name = "YlOrRd")

europe_map <- ggplot(data = world) +
  geom_sf(aes(fill = cut(Value, breaks = breaks, labels = labels, include.lowest = TRUE)), color = "black") +
  scale_fill_manual(values = c("gray50", palette), na.value = "gray50", name = "Violence against Women") +
  labs(title = "Prevalence of Lifetime Violence against Women in Europe", subtitle = "Data Source: violence_women.csv") +
  theme_minimal() +
  coord_sf(xlim = c(-15, 45), ylim = c(30, 70), expand = FALSE)

print(europe_map)

ggsave("Europe_Violence_Against_Women_Map.png", plot = europe_map, width = 10, height = 10)


```

# CONSOLIDATION EXCERCISE 2: heatmaps

File AIRBNB_BCN.Rdata contains information about the AirBnB offers in the city of Barcelona. bcn_districts.shp is a shapefile with the delimitation by districts of Barcelona.

1 - Read both files into R and answer the following questions: Do this sf object have the same CRS? Act in consequence.

2 - Produce a heatmap with the location of the airbnb accomodations.

3 - Add a map tile as map background and the delimitation of the districts.

4 - Focus the final map on the city centre, as shown in the map below.

5 - Save your map as an image.

```{r}
```