---
title: "Homework 7"
author: "Brayan Duran Medina"
output: html_document
---

# CONSOLIDATION EXCERCISE 1: choropleth maps

1 - Read “violence_women.csv” file into R.

2 - Join the csv data to your world sf object.

3 - Replace NA values in column value with zeros. Hint:

shp_violence$Value[is.na(shp_violence$Value)] <- 0

4 - Create some pretty breaks for your data, as the ones in the image below. Equal 0 to No Data.

5 - Create a color palette for your map and plot in showing only the cases of Europe, as in the image below.

6 - Save your map as an image.

```{r}
```

# CONSOLIDATION EXCERCISE 2: heatmaps

File AIRBNB_BCN.Rdata contains information about the AirBnB offers in the city of Barcelona. bcn_districts.shp is a shapefile with the delimitation by districts of Barcelona.

1 - Read both files into R and answer the following questions: Do this sf object have the same CRS? Act in consequence.

2 - Produce a heatmap with the location of the airbnb accomodations.

3 - Add a map tile as map background and the delimitation of the districts.

4 - Focus the final map on the city centre, as shown in the map below.

5 - Save your map as an image.

```{r}
```