---
title: "Homework 3"
author: "Brayan Duran Medina"
output: html_document
---

## EX 1: DONUTS ######
 Using data_S2, please produce a facet donut-plot showing the percentage of 
 Spanish-born and foreign-born population living in each region (COM) of Spain
 in 2016. 
 Save your plot as an image.

 One soda, beer or glass of wine invited by the instructor to the first
 person who, programmatically, manage to order de facets in ascendant order with
 respect to percentage of foreign-born population living in each region. 

```{r}
```

## EX 2: JOYPLOTS ########
 Read countries.csv and e0M.csv into R
 Use the countries in countries.csv to filter e0M
 Produce a joy plot (ridges) setting the time interval on the y-axis and the 
 values on the x-axis. Maybe you want to take a look:
 https://cran.r-project.org/web/packages/ggridges/vignettes/introduction.html
 Save your plot as an image.

```{r}
```

## EX 3: LOLLIPOP #######
 Read CoDB_2021.csv into R
 Create a faceted lollipop plot with the proportion of 1-person (HS01), 2-3persons (HS12),
 4-5persons (HS13) and 6+persons (HS14) households in each country. 
 Please, express the proportion as a percentage. Hint: labels = scales::percent
 Save your plot as an image. 

```{r}
```

## Ex 4: SMOOTHED DOTS #####
 Read CoDB_NDS.csv into r
 Create a new data frame selecting columns 2 to 6 and HS01 to HS11 (proportion 
 of households of 1,2,3...10 and 11+ persons) and keep the cases of LATIN-AMERICA
(C3) when the source of the data (S2) is equal IPUMS
 Using variable C4 for faceting, plot a smoothed dot plot with the value of 
 indicators (HS01: HS11) on the yaxis and the time (T1) in the xaxis. 

```{r}
```