---
title: "Homework 4"
author: "Brayan Duran Medina"
output: html_document
---

## EX 1: DONUTS ######
 Using data_S2, please produce a facet donut-plot showing the percentage of 
 Spanish-born and foreign-born population living in each region (COM) of Spain
 in 2016. 
 Save your plot as an image.

 One soda, beer or glass of wine invited by the instructor to the first
 person who, programmatically, manage to order de facets in ascendant order with
 respect to percentage of foreign-born population living in each region. 

```{r, cache = TRUE}

library(dplyr)
library(tidyr)
library(readxl)
library(ggplot2)

load("data/data_s2.Rdata")

data_S2 <- data

data_2016 <- subset(data_S2, YEAR == 2016)

data_2016$total_population <- rowSums(data_2016[, c("POP_SPANISH", "POP_LATINAMERICA", 
                                                    "POP_WESTERNEUROPE", "POP_EASTERNEUROPE", 
                                                    "POP_AFRICA", "POP_ASIA", "POP_OTHERS")])

data_2016$spanish_population <- rowSums(data_2016[c("POP_SPANISH")])

data_2016 <- data_2016 %>% group_by(COM) %>% summarise(total_population = sum(total_population),
                                                       spanish_population = sum(spanish_population))

data_2016 <- data_2016 %>%
  mutate(foreign_population = total_population - spanish_population,
         spanish_percentage = (spanish_population / total_population) * 100,
         foreign_percentage = (foreign_population / total_population) * 100)

data_long <- data_2016 %>%
  gather(key = "population_type", value = "percentage", spanish_percentage, foreign_percentage)

data_long$COM <- factor(data_long$COM, levels = data_2016$COM[order(data_2016$foreign_percentage)])

data_long <- data_long %>%
  group_by(COM) %>%
  mutate(pos = cumsum(percentage) - percentage / 2,
         label = paste0(round(percentage, 2), "%"))

colors <- c("spanish_percentage" = "#9ac3e1", "foreign_percentage" = "#f09797")

ggplot(data_long, aes(x = 2, y = percentage, fill = population_type)) +
  geom_bar(stat = "identity", width = 1) +
  geom_text(aes(label = label, y = pos), color = "black", size = 3) +
  coord_polar(theta = "y", start = 0) +
  facet_wrap(~ COM, ncol = 4) +
  scale_fill_manual(values = colors, labels = c("Spanish-born", "Foreign-born")) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    plot.title = element_text(size = 12, margin = margin(b = 10)),
  ) +
  labs(fill = "Group", 
       title = "Percentage of Spanish-born and Foreign-born Population by Region in Spain (2016)") +
  xlim(0.5, 2.5)

ggsave("p1.png", width = 15, height = 8)
```

## EX 2: JOYPLOTS ########
 Read countries.csv and e0M.csv into R
 Use the countries in countries.csv to filter e0M
 Produce a joy plot (ridges) setting the time interval on the y-axis and the 
 values on the x-axis. Maybe you want to take a look:
 https://cran.r-project.org/web/packages/ggridges/vignettes/introduction.html
 Save your plot as an image.

```{r, cache = TRUE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(readxl)
library(readr)
library(ggridges)

countries <- read_csv("data/countries.csv")
e0M <- read_csv("data/e0M.csv")

filtered_e0M <- e0M %>%
  filter(country %in% countries$x)

e0M_long <- filtered_e0M %>%
  gather(key = "time_interval", value = "value", -country, -country_code)

e0M_long$time_interval <- factor(e0M_long$time_interval, levels = rev(unique(e0M_long$time_interval)))

e0M_long <- e0M_long %>%
  filter(time_interval != "last.observed")

p <- ggplot(e0M_long, aes(x = value, y = time_interval, fill = as.numeric(time_interval))) +
  geom_density_ridges(scale = 1, rel_min_height = 0.01, bandwidth = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 5)) +
  scale_fill_gradientn(colours = rainbow(length(unique(e0M_long$time_interval)))) +
  theme_ridges() +
  theme(legend.position = "none",
  panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
  ) +
  labs(title = "Global convergence in male life expectancy at birth since 1950",
       x = "Values",
       y = "Time Interval",
       fill = "Time Interval")

ggsave("p2.png", plot = p, width = 12, height = 8)

print(p)
```

## EX 3: LOLLIPOP #######
 Read CoDB_2021.csv into R
 Create a faceted lollipop plot with the proportion of 1-person (HS01), 2-3persons (HS12),
 4-5persons (HS13) and 6+persons (HS14) households in each country. 
 Please, express the proportion as a percentage. Hint: labels = scales::percent
 Save your plot as an image. 

```{r, cache = TRUE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)

# Read the CSV file
data <- read.csv("data/CoDB_2021.csv")

# Select relevant columns
data <- data %>%
  select(C2, HS01, HS12, HS13, HS14)

# Rename columns for readability
colnames(data) <- c("Country", "1P-Household", "2-3P-Household", "4-5P-Household", "6+P-Household")

# Transform the data into long format
data_long <- data %>%
  pivot_longer(cols = ends_with("Household"), names_to = "Household_Size", values_to = "Proportion")

# Calculate the proportion as a percentage
data_long <- data_long %>%
  mutate(Proportion = Proportion * 100)

# Create the faceted lollipop plot with inverted axes
plot <- ggplot(data_long, aes(y = Household_Size, x = Proportion, color = Country)) +
  geom_segment(aes(y = Household_Size, yend = Household_Size, x = 0, xend = Proportion)) +
  geom_point(size = 3) +
  scale_x_continuous(labels = percent_format(scale = 1)) +
  scale_y_discrete(limits = rev(levels(factor(data_long$Household_Size)))) +
  facet_wrap(~ Country, scales = "free_x") +
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    legend.position = "none",
    panel.spacing = unit(2, "lines")  
  ) +
  labs(title = "Distribution (%) of households by size, 2021",
       y = "Household Size",
       x = "Proportion (%)") +
  theme(axis.text.y = element_text(angle = 0, hjust = 1))

# Save the plot as an image
ggsave("p3.png", plot, width = 15, height = 10)
print(plot)
```

## Ex 4: SMOOTHED DOTS #####
 Read CoDB_NDS.csv into r
 Create a new data frame selecting columns 2 to 6 and HS01 to HS11 (proportion 
 of households of 1,2,3...10 and 11+ persons) and keep the cases of LATIN-AMERICA
(C3) when the source of the data (S2) is equal IPUMS
 Using variable C4 for faceting, plot a smoothed dot plot with the value of 
 indicators (HS01: HS11) on the yaxis and the time (T1) in the xaxis. 

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

df <- read.csv("data/CoDB_NDS.csv")

filtered_df <- df %>%
  filter(S2 == "IPUMS" & C3 == "LATIN-AMERICA") %>%
  select(C4, T1, HS01:HS11)

long_df <- filtered_df %>%
  pivot_longer(cols = starts_with("HS"), names_to = "Household_Size", values_to = "Value")

plot <- ggplot(long_df, aes(x = T1, y = Value, color = Household_Size, fill = Household_Size)) +
  geom_point() +
  geom_smooth(se = TRUE, size = 1, alpha = 0.2) +  # Línea suavizada con sombreado del mismo color
  facet_wrap(~ C4) +
  labs(x = "Time", y = "Value of Indicators", 
       title = "Smoothed Dot Plot of Household Size Indicators Over Time") +
  scale_x_continuous(breaks = seq(1960, 2020, by = 10)) +
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )

ggsave("p4.png", plot, width = 12, height = 6)

print(plot)
```